API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Grammar

For efficiency reasons, the public interface is oriented towards processing
batches of samples rather than single samples per API call. While classification
and regression algorithms can indeed make predictions for single samples,
\sklearn objects are not optimized for this use case. (The few online learning
algorithms implemented are intended to take mini-batches.) Batch processing makes
optimal use of NumPy and SciPy by preventing the overhead inherent to Python
function calls or due to per-element dynamic type checking. Although this might
seem to be an artifact of the Python language, and therefore an implementation
detail that leaks into the API, we argue that APIs should be designed so as not
to tie a library to a suboptimal implementation strategy. As such, batch
processing enable fast implementations in lower-level languages (where memory
hierarchy effects and the possibility of internal parallelization come into
play).

>>>>

For efficiency reasons, the public interface is oriented towards processing
batches of samples rather than single samples per API call. While classification
and regression algorithms can indeed make predictions for single samples,
\sklearn objects are not optimized for this use case. (The few online learning
algorithms implemented are intended to take mini-batches.) Batch processing makes
optimal use of NumPy and SciPy by preventing the overhead inherent to Python
function calls or due to per-element dynamic type checking. Although this might
seem to be an artifact of the Python language, and therefore an implementation
detail that leaks into the API, we argue that APIs should be designed so as not
to tie a library to a suboptimal implementation strategy. As such, batch
processing enables fast implementations in lower-level languages (where memory
hierarchy effects and the possibility of internal parallelization come into
play).
